Title

### 2023-10-22 Response to Reviewers.tex

\section*{Reviewers' General Comments}

\textbf{Reviewer 1:} \\

\textbf{
The paper presents two results: 1. A way to simulate
parametric Pauli Channels using a gate-based formalism, useful for
quantum computation, and 2. An investigation on the class of
parametric Pauli Channels that can be parametrised by acting only on
one qubit via one parameter.
The full detailed comments on the paper are attached in the pdf file.
My general comments are the following:
\begin{itemize}
\item[1.]The two aforementioned results are disjointed and completely
lacking in motivation. The entire logic of the paper is obscure, and
seemingly lacks any ground for the results to be useful in any way.
\item[2.] The simulation on the IBM quantum computer is irrelevant, and does
not prove neither the validity of the decomposition (as it fails for
most of the range of operations) nor it is quantifiying any relevant
parameter (noise for example). Data from those experimental runs and
complete methodology for calculating the diamond norm is also missing.
\item[3.] The claims are vague, and the mathematical formalism is vague, with
strong abuse of notation and non-strict definitions and theorems.
There are also many spelling mistakes and refuses, even in the
formulas.
\item[4.] The analysis on the 1-parametrisation is lacking a discussion on
what happens at higher than 2 dimensions.
\end{itemize}
For the aformenetioned reasons, I cannot reccomend this paper for
publication. I suggest the following three course of actions:
\begin{itemize}
\item[1.] Separate the two main results.
\item[2.]Improve the tightness of the mathematical formalism.
\item[3.]  Find an application of the generalised Pauli Channels that can be
effectively simulated with the methodology.
\end{itemize}
}

We thank the first reviewer for the time spent carefully 
reviewing the manuscript, and the opinions regarding it.
We have made major changes in the manuscript following your comments and recommendations. 
Some of the general changes we made are explained in the following list
and then we respond to more specific comments
throughout the text.
\begin{itemize}
\item We rewrote big parts of the introduction to make more clear the logic of the paper. 
We begin the paper by presenting the theory of Pauli channels, 
and then present the first result, which is the algorithm for simulating them on a quantum computer.
With that algorithm in mind, we seek to generalize it to Pauli dynamical maps, 
so as to include continuous transformations of the 
N-qubit system. This goal leads us to
focus on parametrized quantum circuits and then to consider
what can be done with only moving one parameter.
\item We added the data and code from the IBM quantum computer simulations
to a Github repository.
\item We improved the tightness of the formulation by adding
a more mathematical definition of 1PR circuits and
rephrasing the proof of theorem 2 to make it more clear. 
\item In section 5 of the paper we expanded on the examples for Pauli dynamical maps
that can be implemented with a 1PR circuit.
These Pauli dynamical maps are well-known and we prove here
that they can be done with only moving one parameter in the circuit.
Furthermore, we also implemented these dynamical circuits on IBM's using a 1PR circuit.

\end{itemize}

@@

\textbf{While the implementations appear to be mathematically sound, there
appears to be a lack of comparisons between the actual channel
implemented and the target channel. There is only one Fig. 3 that
shows the diamond fidelities for homogenously-chosen single-qubit
unparametrized Pauli target channels within the tetrahedron region.
This is a nice plot that reveals the realistic errors coming from the
IBM quantum cloud, namely that the single-qubit Pauli channels
corresponding to the central part, which I presume are the
depolarizing channels, have the highest diamond fidelity.}

\textbf{
Besides this plot, the authors however did not show the performance of
their algorithms for larger number of qubits, and there are no
performance plots for dynamical Pauli-channel implementations. For a
further evaluation as to whether the algorithms are scientifically
practical, at least a plot on two-qubit Pauli channels and one on
two-qubit dynamical Pauli channels. My take is that because the
unitary operators A and B are too sophisticated for hardware
implementations, since they are even more complicated than single
controlled unitary operators, the fidelity could be very strongly
peaked around the zero of the pseudo Bloch-vector space for multiqubit
systems. If the overall system is too large even for simulating
two-qubit channels (due to the ancillas), then classical numerical
simulations are sufficient.}

\textbf{
In any case, after supplying the performance plots, I believe that the
algorithms and performance plots shall supply a fair presentation on
the scientific soundness of this work.} \\

We thank the second reviewer for the detailed analysis
of our manuscript and the comments made. 
Following the recommendations, we 
added section 3.3 in which we simulate a two qubit Pauli dynamical map 
and show that the fidelities are still reasonably high. 
Furthermore, we also supplied plots of the simulation of the
three Pauli dynamical maps studied in section 5. 
For each of these simulations, we used the proposed 1PR circuit and plotted the fidelities for
different channels along the dynamical map.

\section*{Comments throughout the text}

Here we present the comments made by the reviewers throughout the text 
and respond to each of them individually.
The comments are written in bold and our response in regular font.

@@

\begin{enumerate}
\item \textbf{I fail to see the point here, the logic of the paper is: 
1. ``open quantum systems can be modeled through a class of channels representing he various types of decoherence.'' 2. ``Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.''
3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them.}

\textbf{What I am missing is what do we learn by doing it which cant be learned by actually performing the Pauli channel onto a quantum system? For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial. Why would I need to decompose (not even effectively for any channel) the pauli channels to match a gate based description? Which class of problems can we simulate that cannot be simulated otherwise? Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)}

\textbf{Intuitively, it seems incredibly harder resource wise to create the sum b|gamma> superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective. }\\

We rewrote parts of the introduction to make the objective of the manuscript more clear. 
First of all, one of the principal objectives of quantum computers nowadays
is to use them for simulation of quantum processes,
and out of all quantum processes, decoherence is one of the most important and prevalent.
That is why we chose to simulate Pauli channels, which are one of the
simplest descriptions of decoherence. 
Important characteristics about the algorithm proposed for Pauli channels
are its simplicity and generality.
We choose to represent the channel using a gate-based formalism because
of it being one of the most common and general ways of
representing quantum algorithms.

Furthermore, the simplicity and generality of the circuit proposed allows us to
naturally generalize it to Pauli dynamical maps by just
adding movable parameters to the circuit.
Finally, we show the general result of what parametrized quantum operations can be done 
moving only one parameter, which experimentally could translate
to having to adapt only one setting of an experiment
to simulate a quantum operation.

@@

\item \textbf{ Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}\\

A sentence was added to the text mentioning how we get to the equation by starting with the relation $[\sigma_\alpha,\sigma_\beta] = 2 i
\epsilon_{\alpha \beta \gamma} \sigma_\gamma$.
After using this equation on $\sigma_{\alpha} \sigma_{\gamma} \sigma_{\alpha}$, the Levi-Civita tensors are summed out and we are left with:
\begin{equation*}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (2\delta_{\alpha \gamma}-1)(2\delta_{\alpha 0}-1)(2\delta_{\gamma 0}-1)
\end{equation*}
We believe that writing matrix $A$ explicitly is simpler than this expression.

@@

\item \textbf{Eq 2} \\

The correct equation is indeed equation 1, since we are referring to the fact that 
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
has the form of $\dfrac{1}{2} \sum_{\alpha} r_{\alpha} \sigma_{\alpha}$, only with the
$r_{\alpha}$ replaced by $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.

\item \textbf{At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism. The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \\

We added a few lines at the beginning of section 3 defining the concept of quantum circuit.
We  mention that quantum circuits are a representation of computation on quantum systems, which applies a unitary operator $U$.

@@

\item  \textbf{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise.}\\

The algorithm works to some extent for all Pauli channels, and how well
it does or does not work is quantified by the fidelity.
Indeed, the result we got is that it works much better for channels that are depolarizing
and less well as we get closer to unitary channels.

@@

\item \textbf{Why?}\\
We rephrased the sentence to make the point more clear
and explained that as a consequence of the circuit being usable in general for any Pauli channel,
it implements unitary channels in a very roundabout way.

\item \textbf{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.} \\

\item \textbf{But this is a severe disadvantage, that begs the question: what is the advantage?} \\

The advantages are that it is a straightforward, concrete and general way
of simulating Pauli channels.
Being general gives the possibility to later use it for Pauli dynamical maps by only needing to vary the parameters
and not the design of the circuit in general.

@@

\item \textbf{Normal}\\

They are only orthogonal, since their individual norms are not equal to $1$.

\item \textbf{Again, this is not a conclusion from theorem 1. This is literally Definition 1. Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N. Then the matrix representation of the operators is a $2^n\times 2^n$ matrix which is applied to the state j. The explanation in words in not sufficient.} \\

We rephrased the first paragraph of the proof to make it more clear when we use the result of theorem 1. 
Basically, we first use definition 1 to say that the circuit has the form $ARB$,
and then the result of theorem $1$
to conclude that $R$ is in particular a $\sigma_3$ rotation
of angle $2s$ applied to the last qubit.\\

\item \textbf{True only if the initial j states are normalised, but they were undefined.}\\

@@

\item \textbf{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?}\\

We changed the phrasing to make it more clear that $A$ and $B$ 
are restricted to act in a particular way on the last 3 and first qubit respectively.
Besides from that, the remaining parts of the operators $A$ and $B$ can be chosen arbitrarily, 
with the only restriction that the resulting matrices are unitary. \\

\item  \textbf{Please, at least give an example of this semiarbitrary construction of A and B.}\\

We added examples of these matrices for the three particular dynamical maps shown in the next section. \\

@@

We rephrased this part to make it clearer. The idea is that we are searching for the matrices $A$ and $B$ such
that for given vectors $|a\rangle, |b\rangle, |c\rangle$, the circuit creates
the state $e^{is(p)} |a \rangle + e^{-is(p)} |b \rangle + |c\rangle$.
In this part, we show that with the matrices $A$ and $B$ we constructed,
we indeed create said state.
That way, given any curve of states that can be done with a 1PR circuit
according to theorem 2, here we show how
to actually create said circuit (that is, which matrices $A$, $B$ to select).\\

\item \textbf{To see what?} \\

As said before, to see that the selection of matrices $A$, $B$ creates 
the curve of states we wanted.
This part of the text has been rewritten to make it clearer.\\

\item \textbf{So this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \\

@@

This is an intermediate step, but as said in the previous questions, 
we are proving that the selection of $A$ and $B$ for given vectors $|a\rangle, |b\rangle, |c\rangle$ 
indeed works to create the state
$e^{is(p)} |a \rangle + e^{-is(p)} |b \rangle + |c\rangle$.\\

\item \textbf{To be consistent with the previous formalism, the states should be 0,1,2,3}\\

We made the change.\\

\item \textbf{There is literally one parameter in one qubit, of course it depends on one parameter...
 how can this be a result?} \\

The result is that they needed  to move just one parameter to implement 
many Pauli channels of the bit flip map.
For other maps, they may need to move more than one parameter to 
implement all the channels in the map. 
However, just as we showed that the bit flip map can be done with a 1PR circuit,
they implemented the map using one parameter.\\

@@

 \item  \textbf{This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example)} \\

Some of the examples given (depolarizing, bit flip, phase flip, bit-phase flip) are very well known 
Pauli maps.
We also included random examples with the purpose of seeing how some general maps that 
can be implemented with a 1PR circuit look like.

 \item  \textbf{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit. I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so.. what is the applicability of the theorem for higher dimensions?} \\

We added a paragraph in the conclusion talking about that.
There we argue that for bigger systems, the space of dynamical maps
that can be implemented with a 1PR circuit
is a smaller part of the whole space of dynamical maps.
However, some of the most paradigmatic maps will still be implementable this way.

\item \textbf{Imprecise} \\

We have rephrased parts of the conclusion to make it more clear.

\item \textbf{This reasoning I miss, simplifying for achieving what goal? } \\

We rephrased the conclusion to make it more clear. We wanted to reduce the number of parametrized gates
so as to have only one parameter that works as a kind of knob to move around in the channels forming
a dynamical map.

\item\textbf{ There is no quantification of this, it´s not even the focus of the paper.}  \\

We have a quantification of the fidelity of the implementation of different Pauli channel and dynamical maps.
 Even though it is indeed not the focus of the paper, we believe it
 is an important enough part of it as to mention it again in the conclusion.

\item \textbf{Citation required here.}
We added a citation.
\end{enumerate}

### 2023-11-08 main.tex
fix bug, for realz

\cpnote{Iteara de nuevo Tomas:
However, in this article, our main goal is not to implement Pauli channels, but to study and implement Pauli dynamical maps, which are continuous parametrized curves of Pauli channels. 
These maps can be used to model continuous change of a qubit instead of only discrete jumps.
Implementing these maps will lead us to study  quantum algorithms with free parameters, 
something that is common in areas such as quantum machine learning~\cite{Benedetti}.
This can be done using parametrized quantum circuits, which consist of quantum
circuits in which one or more operations depend on a free parameter. }

\cpnote{Porfa mete esto en el parrafo donde va la estructura:
Our study of such circuits for the use of simulating Pauli dynamical maps will
lead us to theorem 2, in which we find general condition for any parametrized
transformation (for example, a Pauli dynamical map) to be achievable on a
quantum circuit with only one single-qubit rotation dependent on the parameter.
Said parameter is in some sense a knob that we can control to continuously
perform the transformation by only having to move one number. }

\tbnote{
Continuing with this previous work done to simulate quantum processes, in this article we 
propose a quantum algorithm for simulating Pauli channels
and implement it on one of IBM's quantum computers.
The algorithm proposed is straightforward and can be used for any Pauli channel by only changing a couple of 
parameters in the operations it performs. 
To represent the algorithm, we use a quantum circuit, which is a common
way of representing algorithms intended for quantum computers.~\cite{chuangbook}.  }

\tbnote{ Furthermore, we will also simulate Pauli dynamical maps, which are continuous parametrized curves of Pauli channels.
These maps can be used to model a continuous change of a qubit instead of only discrete jumps. 
The generality of the algorithm proposed for Pauli channels will be very useful in this part, since then
using for dynamical maps will come very naturally.
Implementing these maps will lead us to study quantum algorithms  with free parameters, 
something that is common in areas such as quantum machine learning~\cite{Benedetti}.
This can be done using parametrized quantum circuits, which consist of quantum
circuits in which one or more operations depend on a free parameter. }

\cpnote{dejar solo un parrafo de estructura:} 
\tbnote{Aqui está:}

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a general and straightforward quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for some single and two-qubit Pauli channels.
Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem, which  sets
the mathematical conditions for the transformations that can be done using a
parametrized circuit with the restriction that only a controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in section
\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

\revnote{I fail to see the point here - the logic of the paper is: % {{{
1."open quantum systems can be modeled through a class of channels representing
he various types of decoherence. 2. Quantum circuits are a convenient
gate-based formalism that is well understood and has an extensive body of work,
and experimentally accessible.  3. We map (generalised) Pauli channels onto
quantum circuits, as a way to simulate them. \\
What I am missing is what do we learn by doing it which can't be learned by
actually performing the Pauli channel onto a quantum system? For example,
applying well controlled sx, sy, sz operations and their coherent parametric
combination using a photonic polarisation or path encoding is experimentally
trivial. Why would I need to decompose (not even effectively for any channel)
the Pauli channels to match a gate based description? Which class of problems
can we simulate that cannot be simulated otherwise? Is there any advantage (for
example in speed up, resources like ancillas required, resistance to unwanted
noise etc..?)\\
Intuitively, it seems incredibly harder resource wise to create the sum
$b|gamma\rangle$ superposition state needed for the ancilla, just for the sake
of having it into a "quantum circuit" perspective.} % }}}

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. \revnote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. } 
\tbnote{Contestar en la carta que funciona hasta cierto punto para todos los canales propuestos
y que se cuantifica qué tan bien funciona o no usando la fidelidad}
 This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
Moreover, the algorithm of \fref{Fig2} is not optimal for
unitary channels (that is, the channels corresponding to the vertices of the
tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
baja segun la imagen, por lo que podemos ver que los unitarios
tienen una fid baja.} 
\tbnote{Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
channels in the edges of the tetrahedron, which corresponds to unitary channels. }
 These simple channels could be accomplished more
efficiently by simply applying the corresponding Pauli operator directly. \revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
\tbnote{Este comentario se conecta con lo del 
primer comentario, que no sé bien cómo contestar.}
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
\tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
{\color{green} This disadvantage comes from the fact
that the circuit is applicable to any Pauli channel, which that means that sometimes
it is not the most straightforward algorithm to simulate a Pauli channel.
However, the main advantages are that the algorithm is simple, and if we want 
to simulate many Pauli channels (for example,
for simulating a Pauli dynamical map as we will see later),
we only have to change a couple of angles in the circuit to move between 
different Pauli channels and not completely reconstruct the circuit. 
And as we will see, sometimes only changing
one angle in the circuit will be enough.}\\
$\;$\\

@@

% }}}
%\section{Supporting information} % {{{
%
%
%% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
%\paragraph*{S1 Code.}
% \label{S1_code}
% {\bf Simulation of Pauli Channels.} Python code for the simulation of Pauli channels on IBM's quantum computers.
%% 
% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}

%
%\section{Acknowledgments} % {{{
%Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.

>>>>

In this article we propose a quantum algorithm for simulating Pauli channels
and implement it on one of IBM's quantum computers.  The algorithm proposed is
straightforward and can be used for any Pauli channel by only changing a couple
of parameters in the operations it performs.  To represent the algorithm, we
use a quantum circuit, which is a common way of representing algorithms
intended for quantum computers.~\cite{chuangbook}.  Furthermore, we will also
simulate Pauli dynamical maps, which are continuous parametrized curves of
Pauli channels.  These maps can be used to model a continuous change of a qubit
instead of only discrete jumps.  The generality of the algorithm proposed for
Pauli channels will be very useful in this part, since then using for dynamical
maps will come very naturally.  Implementing these maps will lead us to study
quantum algorithms  with free parameters, something that is common in areas
such as quantum machine learning~\cite{Benedetti}.  This can be done using
parametrized quantum circuits, which consist of quantum circuits in which one
or more operations depend on a free parameter.

We start by providing the definition of quantum channels, the general framework
used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
Our first objective is to present a general and straightforward quantum algorithm capable of simulating
Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
for a Pauli Channel}, where we also demonstrate its implementation using IBM's
quantum computers for several single and two-qubit Pauli channels.
Expanding beyond Pauli channels, we introduce the concept of Pauli
dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
study parametrized quantum channels, aiming to adapt the algorithm developed
for channels to dynamical maps\cpnote{Me parece que las dos frases anteriores 
dicen casi lo mismo. Poner una sola frase}.  Furthermore, we contribute to the body of work
related to parametrized quantum circuits by establishing a theorem, which  sets
the mathematical conditions for the transformations that can be done using a
parametrized circuit with the restriction that only a controlled single-qubit
rotation in the circuit may depend on the parameter.  Finally, in section
\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
dynamical maps that fulfill the conditions of theorem \ref{theorem2}.

@@

% \revnote{I fail to see the point here - the logic of the paper is: % {{{
% 1."open quantum systems can be modeled through a class of channels representing
% he various types of decoherence. 2. Quantum circuits are a convenient
% gate-based formalism that is well understood and has an extensive body of work,
% and experimentally accessible.  3. We map (generalised) Pauli channels onto
% quantum circuits, as a way to simulate them. \\
% What I am missing is what do we learn by doing it which can't be learned by
% actually performing the Pauli channel onto a quantum system? For example,
% applying well controlled sx, sy, sz operations and their coherent parametric
% combination using a photonic polarisation or path encoding is experimentally
% trivial. Why would I need to decompose (not even effectively for any channel)
% the Pauli channels to match a gate based description? Which class of problems
% can we simulate that cannot be simulated otherwise? Is there any advantage (for
% example in speed up, resources like ancillas required, resistance to unwanted
% noise etc..?)\\
% Intuitively, it seems incredibly harder resource wise to create the sum
% $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake
% of having it into a "quantum circuit" perspective.} % }}}

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. 
% \revnote{So another way to see this is that the simulation through the
% proposed decomposition works only for depolarising channels, and fails
% otherwise. } 
% \tbnote{Contestar en la carta que funciona hasta cierto punto para todos los
% canales propuestos y que se cuantifica qué tan bien funciona o no usando la
% fidelidad}
This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
% Moreover, the algorithm of \fref{Fig2} is not optimal for
% unitary channels (that is, the channels corresponding to the vertices of the
% tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
% baja segun la imagen, por lo que podemos ver que los unitarios
% tienen una fid baja.} 
% \tbnote{
Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
channels in the edges of the tetrahedron, which corresponds to unitary channels. 
% }
 These simple channels could be accomplished more
efficiently by simply applying the corresponding Pauli operator directly. \revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
\tbnote{Este comentario se conecta con lo del 
primer comentario, que no sé bien cómo contestar.}
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
\tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
{\color{green} This disadvantage comes from the fact
that the circuit is applicable to any Pauli channel, which that means that sometimes
it is not the most straightforward algorithm to simulate a Pauli channel.
However, the main advantages are that the algorithm is simple, and if we want 
to simulate many Pauli channels (for example,
for simulating a Pauli dynamical map as we will see later),
we only have to change a couple of angles in the circuit to move between 
different Pauli channels and not completely reconstruct the circuit. 
And as we will see, sometimes only changing
one angle in the circuit will be enough.}\\
$\;$\\

@@

% }}}
%\section{Supporting information} % {{{
%
%
%% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
%\paragraph*{S1 Code.}
% \label{S1_code}
% {\bf Simulation of Pauli Channels.} Python code for the simulation of Pauli channels on IBM's quantum computers.
%% 
% \paragraph*{S2 Fig.}
% \label{S2_Fig}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 File.}
% \label{S1_File}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Video.}
% \label{S1_Video}
% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Appendix.}
% \label{S1_Appendix}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% 
% \paragraph*{S1 Table.}
% \label{S1_Table}
% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.
% }}}
%
%\section{Acknowledgments} % {{{
%Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.
